### 2019-01-03 manuscript/manuscript.rmd
updated partition comparison code

```{r preliminaries}
library( tidyverse )
library( magrittr )
library(viridis)
library(ape)

@@

```{r taxon_mapping_across_studies}

@@

```{r taxon_mapping}

@@

Dpart = 
	read_tsv("../reconciliation/blast/graphs/partitions_graph.tsv") %>% 
	mutate( node1 = paste(mscript1, dataset1, part1, sep = ':') ) %>% 
	mutate( node2 = paste(mscript2, dataset2, part2, sep = ':') )

Dpart_self = Dpart %>% 
	filter( node1==node2 ) %>%
	select( mscript1, dataset1, part1, node1, count )

ggplot( Dpart_self ) + geom_density(aes(count))

@@

D_source = Dpart %>%
  distinct(node1, .keep_all = TRUE ) %>%
	select( node1, mscript1, dataset1, part1 ) %>%
  dplyr::rename(label = node1, mscript = mscript1, dataset = dataset1, part = part1 )

D_dest = Dpart %>%
  distinct(node2, .keep_all = TRUE ) %>%
	select( node2, mscript2, dataset2, part2 ) %>%
  dplyr::rename(label = node2, mscript = mscript2, dataset = dataset2, part = part2 )

@@

#library( network )

#gene_network = network( edges, directed=FALSE, vertex.attr = nodes, matrix.type = "edgelist", ignore.eval = FALSE)
#
#gene_matrix = as.sociomatrix(gene_network)

#library( MCL )

#gene_clusters = mcl( x=gene_matrix, addLoops = TRUE )

library(igraph)
gene_igraph = graph_from_data_frame(d = edges, vertices = nodes, directed = FALSE)
gene_clusters = clusters(gene_igraph, mode=c("weak", "strong"))

@@

# Investigate commencted components of genes (ie partitions) that include multiple members fromt he same matrix
D = nodes %>% group_by( mscript, dataset, cluster ) %>% summarise(n=n()) %>% arrange(desc(n))
D %>% print(n=100)

>>>>

```{r preliminaries}
library( tidyverse )
library( magrittr )
library(viridis)
library(ape)
library(igraph)

@@

```{r taxon_mapping_across_studies, eval=FALSE}

@@

```{r taxon_mapping, eval=FALSE}

@@

Dpart = 
	read_tsv("../reconciliation/blast/graphs/partitions_graph.tsv") %>% 
	mutate( node1 = paste(matrix1, part1, sep = ':') ) %>% 
	mutate( node2 = paste(matrix2, part2, sep = ':') )

# Hits to self not included anymore, so skip this bit
# Dpart_self = Dpart %>% 
#	 filter( node1==node2 ) %>%
#	 select( matrix1, part1, node1, count )
# ggplot( Dpart_self ) + geom_density(aes(count))

@@

D_source = Dpart %>%
  distinct(node1, .keep_all = TRUE ) %>%
	select( node1, matrix1, part1 ) %>%
  dplyr::rename(label = node1, matrix = matrix1, part = part1 )

D_dest = Dpart %>%
  distinct(node2, .keep_all = TRUE ) %>%
	select( node2, matrix2, part2 ) %>%
  dplyr::rename(label = node2, matrix = matrix2, part = part2 )

@@

gene_igraph = graph_from_data_frame(d = edges, vertices = nodes, directed = FALSE)
gene_clusters = clusters(gene_igraph, mode=c("weak", "strong"))

@@

# Investigate commencted components of genes (ie partitions) that include multiple members fromt he same matrix
D = nodes %>% group_by( matrix, cluster ) %>% summarise(n=n()) %>% arrange(desc(n))
D %>% print(n=100)
